---
title: "Cross Validation"
author: "Lectured by Jeff Goldsmith"
date: "2022-11-15"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(modelr)
library(mgcv)
```

# Model selection

When you have lots of variables, you have to choose which ones will go in your model.

For nested models, you have tests
* You have to be worried about multiple comparisons and "fishiing"

For non-nested models, you don't have tests
* AIC/BIC/etc are traditional tools 
  * To understand what [AIC](https://www.scribbr.com/statistics/akaike-information-criterion/) is, click on it.
* Balance goodness of fit with "complexity"

# Cross validation

Randomly split your data into "training" and "testing"
- "Training" is data you use to build your model
- "Testing" is data you use to evaluate out-of-sample fit
- Exact ratio depends on data size, but preferably 80/20

```{r}
# Create a dataframe with 100 random nonlinear numbers (x-variable) and a y-variable that depends on x-variable.
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

```{r get this by hand}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")
```

```{r}
train_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() +
  geom_point(data = test_df, color = "red")
```

Let's try to fit three models.

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Let's make predictions and compute Root Mean Square Errors (RMSEs).

```{r}
rmse(linear_mod, test_df)
rmse(wiggly_mod, test_df)
rmse(smooth_mod, test_df)

# Lower values mean better. We want lower prediction error!
```
Is this error prediction due to chance or it's significant?

## Can we iterate?

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    linear_fits = map(.x = train, ~lm(y ~ x, data = .x)))
```



