---
title: "Cross Validation"
author: "Lectured by Jeff Goldsmith"
date: "2022-11-15"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(modelr)
library(mgcv)
```

# Model selection

When you have lots of variables, you have to choose which ones will go in your model.

For nested models, you have tests
* You have to be worried about multiple comparisons and "fishiing"

For non-nested models, you don't have tests
* AIC/BIC/etc are traditional tools 
  * To understand what [AIC](https://www.scribbr.com/statistics/akaike-information-criterion/) is, click on it.
* Balance goodness of fit with "complexity"

# Cross validation

Randomly split your data into "training" and "testing"
- "Training" is data you use to build your model
- "Testing" is data you use to evaluate out-of-sample fit
- Exact ratio depends on data size, but preferably 80/20

```{r}
# Create a bunch of random nonlinear numbers
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

```{r}

```


